%! Author = aymanhki
%! Date = 2025-01-10

\documentclass{article}
\usepackage[margin=0.2in]{geometry} % Correctly specify margins instead of 'cm'
\usepackage{xcolor} % Improved compatibility
\usepackage{hyperref}
\usepackage{fontawesome}
\usepackage{setspace}

\hypersetup{
    breaklinks=true,
    colorlinks=true,
    linkcolor=cyan,
    urlcolor=black
}

\definecolor{contactgray}{rgb}{0.3,0.3,0.3}

\newcommand{\name}[1]{
    \begin{center}
    \textsc{\Huge #1}
    \end{center}
}

\newcommand{\contact}[1]{
    \begin{center}
    \color{contactgray}{\small #1}
    \end{center}
}

\begin{document}
    \pagestyle{empty}

    \doublespacing

    \begin{center}
        \name{Ayman Agamy}
        \contact{
            \href{mailto:agamyahk@myumanitoba.ca}{\faEnvelope\ agamyahk@myumanitoba.ca}
            \hspace{0.1cm} |
            \hspace{0.1cm} \href{tel:+14312759377}{\faMobile\ +1 431-275-9377}
            \hspace{0.1cm} |
            \hspace{0.1cm} \href{https://www.linkedin.com/in/ayman-agamy/}{\faLinkedinSquare\ ayman-agamy}
            \hspace{0.1cm} |
            \hspace{0.1cm} \href{https://github.com/Aymanhki}{\faGithubSquare\ aymanhki}
        }
    \end{center}

    \noindent
    \textbf{\today}

    \noindent
    Just Eat Takeaway.com

    \noindent
    Re: Bilingual (FRENCH AND ENGLISH) Operations Specialist (R\_034166)

    \vspace{1em}

    \noindent
    I am writing to submit my candidature for the Bilingual Operations Specialist position at Just Eat Takeaway.com.
    Through both academia and professional experience, I have become familiar with many of the technologies employed
    by your diverse team of professionals. My familiarity with Just Eat extends beyond ordering food on a weekly
    basis; during my tenure at 7-Eleven, I directly engaged with Skip The Dishes orders, preparing and ensuring
    timely deliveries for numerous customers. This hands-on experience with the customer, driver, and operational
    interfaces has provided me with a comprehensive understanding of the intricate dynamics and the importance of
    streamlined processes. I am particularly drawn to Just Eat's innovative approach to food delivery and its
    commitment to providing customers with an exceptional experience. Having researched the company extensively, I am
    impressed by your dedication to leveraging technology to streamline operations and enhance user interactions. The
    Bilingual Operations Specialist role caught my attention because it aligns perfectly with my skills and
    aspirations, and I am eager to contribute my expertise to further advance Just Eat's mission and objectives. I am
    enthusiastic about the opportunity to bring my technical skills to a team that values both diversity and
    community involvement, and I look forward to the possibility of contributing to your company's ongoing success.

    \vspace{1em}

    \noindent
    In my previous roles, particularly during my time at 7-Eleven, I consistently prioritized customer satisfaction.
    Handling Skip The Dishes orders meant managing various customer inquiries, ensuring timely deliveries, and
    addressing any concerns promptly. This experience not only refined my organizational skills but also emphasized
    the significance of clear communication and proactive problem-solving. I've always believed that exceptional
    customer service is at the heart of any successful operation. Additionally, my background extends to my high
    school years in Egypt where I took French as a second language. This foundational understanding has been further
    enriched during my time in Canada, where I've had opportunities to engage with bilingual environments and enhance
    my proficiency. Being bilingual allows me to connect with a broader range of customers, fostering trust and
    understanding in both English and French settings. I am confident in my ability to bring this dedication,
    bilingual expertise, and customer-centric approach to the Bilingual Operations Specialist role at Just Eat
    Takeaway.com. I am committed to ensuring every interaction aligns with the company's values and contributes to a
    seamless customer experience.

    \vspace{1em}

    \noindent
    Beyond my technical skills, I am a strong collaborator and communicator. My volunteering experience as a Computer
    Science tutor at the University of Manitoba reflects my dedication to fostering knowledge sharing and ensuring a
    clear understanding of complex concepts. It is by solving problems that I grow and develop my coding abilities. I
    always break down the problem into smaller pieces and work my way up using and learning the necessary tools to
    complete it.

    \vspace{1em}

    \noindent
    I am excited about the prospect of being a culture champion and driving change at all levels in the role of an
    Operations Specialist at Just Eat Takeaway.com. Your emphasis on innovation, collaboration, and technological
    advancement resonates with my career aspirations. I appreciate your consideration and look forward to the chance
    to discuss how I can add value to your team.

    \vspace{1em}

    \noindent
    Regards, \\
    Ayman Agamy
\end{document}
